\newglossaryentry{route}{
  name={route},
  description={
      A URL pattern in an application that maps incoming requests to the logic
      or resource that handles them. Defines how a request is processed and what
      response is returned.
    }
}


\newglossaryentry{endpoint}{
  name={endpoint},
  description={
      A specific address in an API defined by an HTTP method and a route. It
      represents one actionable interface for clients, such as \texttt{GET
        /users} or \texttt{POST /login}
    }
}

\newglossaryentry{static site}{
  name={static site},
  description={
      A website whose server responds only to GET requests and serves prebuilt
      files directly from storage. No code execution, templating, or dynamic
      process runs per request; the response depends solely on the requested
      path
    }
}

\newglossaryentry{page}{
  name={page},
  description={
      A single document served at a specific URL on the web, typically an HTML
      response rendered by a browser. A page represents one logical unit of
      content and may include additional assets such as CSS, JavaScript, and
      images. Provides functions for rendering your pages using pandoc, with a
      varying degree of high-levelness.
    }
}

\newglossaryentry{item}{
  name={item},
  description={
      An item is a combination of some content and its Identifier. This way, we
      can still use the Identifier to access metadata
    }
}

\newglossaryentry{store}{
  name={store},
  description={
      A store for storing and retreiving items
    }
}

\newglossaryentry{identifier}{
  name={identifier},
  description={
      A key data type to identify a compiled Item in the Store. Conceptually,
      it's a combination of a file path and a version name. The version is used
      only when a file is compiled within a rule using the version wrapper
      function (the same source file can be compiled into several items in the
      store, so the version exists to distinguish them). Use functions like
      fromFilePath, setVersion, getMatches to build an Identifier
    }
}

\newglossaryentry{template}{
  name={template},
  description={
      Templates are tools to convert items into a string. They are perfectly
      suited for laying out your site
    }
}

\newglossaryentry{rule}{
  name={rule},
  description={
      A rule is basically a function that is waiting to be applied to an item.
      You introduce this rule ``function'' by combining a item and a compiler.
    }
}
